Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-10 analysis/paper/paper.Rmd
fix column formatting in tables

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_f1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>% 
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_f2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_g1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_g2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r if-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_h1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r if-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_h2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r access-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_i1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

@@

```{r access-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_i2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  rename(
    "ROPE\nlow" = "ROPE_low",
    "ROPE\nhigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  set_formatter_type(fmt_double = "%.01f") %>%
  set_formatter(`ROPE %` = function(x) sprintf("%1.f%%", x * 100)) %>%
  autofit()
```

>>>>

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_f1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_f2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_g1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_g2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r if-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_h1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r if-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_h2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r access-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_i1) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```

@@

```{r access-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
equivalence_test(m_i2) %>%
  mutate(Parameter = gsub("b_", "", .$Parameter)) %>%
  mutate(Parameter = gsub("abbreviation", "", .$Parameter)) %>%
  rename(
    "ROPE\nLow" = "ROPE_low",
    "ROPE\nHigh" = "ROPE_high",
    "ROPE %" = "ROPE_Percentage",
    "ROPE Equivalence" = "ROPE_Equivalence",
    "HDI\nLow" = "HDI_low",
    "HDI\nHigh" = "HDI_high"
  ) %>%
  select(-Effects, -Component) %>%
  flextable() %>%
  colformat_num(na_str = "NA") %>%
  colformat_double(
    j = c("CI", "ROPE\nLow", "ROPE\nHigh", "HDI\nLow", "HDI\nHigh"),
    digits = 2
  ) %>%
  set_formatter(
    `ROPE %` = function(x)
      sprintf("%1.f%%", x * 100)
  ) %>%
  autofit() %>%
  set_caption(
    "The effect that the journal titles selected for inclusion had on the probability of pd being negative."
  )
```
